---
title: "p8105_hw1_cw3370"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#Problem 1
Create the data frame 
```{r}
##create a random sample of size 10 from a standard Normal distribution##
vector_num <- rnorm(10)

##create a logical vector indicating whether elements of the sample are greater than 0##
vector_logi <- vector_num > 0

##create a character vector of length 10##
vector_cha <- c("Liverpool","is","the","Primer","League","champion","for","the","2019-2020","season")

##create a factor vector of length 10, with 3 different factor “levels”,the levels is Poor,Improved,Excellent##
vector_factor <- c("Poor","Improved","Poor","Excellent","Improved","Excellent","Poor","Excellent","Improved","Excellent")
vector_factor <- factor(vector_factor,ordered = TRUE,levels = c("Poor","Improved","Excellent"))

##Create the Data Frame##
df1 <- tibble(vector_num , vector_logi , vector_cha , vector_factor)
```

Take the mean of each variable in data frame.

The R can take the mean of numeric variable and logical variable. But it doesn't work for the character variable and factor variable.
```{r collapse=TRUE}
## Take the mean of each variable in df1. var=1 is numeric, var=2 is logical, var=3 is character, var=4 is factor##
mean(pull(df1,var = 1))
mean(pull(df1,var = 2))
mean(pull(df1,var = 3))
mean(pull(df1,var = 4))
```

Convert variables from one type to numeric

The R can convert logical variable and ordered factor variable to numeric. It can also convert the character variable to numeric variable which make all the things become NA. This kind of the conversion is meaningless.

This help explain why R can take the mean value of logical variable since the False means 0 and True means 1. It can also help explain why R cannot take the mean value of character variable and factor variable.
```{r eval=FALSE}
vector1 <- as.numeric(vector_num)
vector2 <- as.numeric(vector_logi)
vector3 <- as.numeric(vector_cha)
vector4 <- as.numeric(vector_factor)
```

#Problem 2
```{r}
##import dataset penguins##
data("penguins", package = "palmerpenguins")
```

Dataset penguins has `r nrow(penguins)` variables, which are `r names(penguins)`. `r names(penguins)[c(1,2,7)]` are factor, `r names(penguins)[c(3,4)]` are number, `r names(penguins)[c(5,6,8)]` are integer. It is a tibble with `r nrow(penguins)` rows and `r ncol(penguins)` cols. The mean flipper length is `r mean(pull(penguins,var=5),na.rm = TRUE)`.
```{r}
## Make a scatterplot by ggplot2. Set the color of point to blue and size of point to 1. Name the titile, x axis and y axis. ##
ggplot(data = penguins, aes(x=bill_length_mm,y=flipper_length_mm)) + 
    geom_point(color="blue",size=1) +
    labs(title ="Scatterplot" , x = "Bill Length (millimeters)" , y = "Flipper Length (millimeters)")

## Save the scatterplot##
ggsave("scatterplot_flipperlength_to_billlength.png",width = 4, height = 4)
```

